---
title: "MATH 216 Homework 5"
author: "Phil Hoxie"
output: html_document
---


## Admistrative:

Please indicate

* Who you collaborated with: Christian Lehner
* Roughly how much time you spent on this HW:
* What gave you the most trouble:
* Any comments you have: 





## Question 1:

* Pick three books from [Project Gutenberg](https://www.gutenberg.org/) and make
a "single-file" Shiny app based on file `App.R`
    + showing the corresponding wordcloud for a given book
    + that has "toggle" functionality to switch between the three books
* Note: Project Gutenberg tends to have older books whose copyright has expired.
* Install all necessary packages on your Middlebury Shiny server account
following the instructions given in Lec16 Shiny.
* Upload your app to the Middlebury Shiny server and replace the NHL link with
the link for your app [https://phoxie58.shinyapps.io/natural_law/](https://www.nhl.com/), so that when you Knit the 
document a working hyperlink shows.

Hints:

* Get your code completely working for a non-Shiny app first, then build your
app slowly.
* If you get stuck, please ask for help sooner rather than later. I don't want 
people spinning their wheels on this HW this late in the semester.
* Consider using `if` and `else` statements to switch out which text to show the
wordcloud for. Note this isn't the only way to do this. Ex:

```{r}
text <- "blah2"
if(text == "blah1"){
  value <- 1
} else if (text == "blah2"){
  value <- 2
} else if (text == "blah3"){
  value <- 3
}
value
```

My code: 
```{r, results='hide'}
library(dplyr)
library(stringr)
library(tm)
library(wordcloud)
library(SnowballC)

locke <-
  readLines("locke.2.treatise.on.gov", encoding="UTF-8") %>%
  as.character()

aquinas <-
  readLines("aquinas.treatise.on.law", encoding="UTF-8") %>%
  as.character()

hobbes <-
  readLines("hobbes.leviathan", encoding="UTF-8") %>%
  as.character()

locke <- locke %>%
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("english")) %>%
  stemDocument() %>%
  stripWhitespace()

hobbes <- hobbes %>%
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("english")) %>%
  stemDocument() %>%
  stripWhitespace()

aquinas <- aquinas %>%
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("english")) %>%
  stemDocument() %>%
  stripWhitespace()
```
```{r}
locke <- VectorSource(locke) %>% 
  Corpus()
wordcloud(locke, scale=c(5,0.5), max.words=25, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "BuPu"))

```
```{r}
hobbes <- VectorSource(hobbes) %>% 
  Corpus()
wordcloud(hobbes, scale=c(5,0.5), max.words=25, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "YlOrRd"))

```
```{r}
aquinas <- VectorSource(aquinas) %>% 
  Corpus()
wordcloud(aquinas, scale=c(5,0.5), max.words=25, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "RdPu"))

```